Title: A proof-of-concept study

### 2022-01-25 paper.tex
update

  As stressed by \citet{Yang2012}, CR diffusion has insignificant effect on the overall morphology of the Fermi bubbles,\
  but only sharpens the edges of the simulated bubbles by the interplay between anisotropic CR diffusion\
  and magnetic fields with suppressed perpendicular diffusion across the bubble surface. Moreover,\
  the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
  little effect on the overall dynamics. For these two reasons,\
  we have ignored the CR diffusion and the magnetic field throughout\
  the simulation.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different cases from left to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disk (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disk has insignificant effect\
             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disk\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear with the disk, and without the disk, the outer bubbles will be tilted,
             indicating the dense disk is crucial for\
             the axis-symmetrically outer bubbles and of the most inner bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

@@

  %\begin{figure*}[ht]
  \begin{figure*}
    \subfigure[(Reproduced with permission from R. Blatt, Rev. Mod. Phys. 87, 1419 (2015).\
               Copyright 2015 American Physical Society.)\
               Synthetic count rate (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps in\
               Galactic coordinates centered on the Galactic center, and the view point .]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
  \caption{The observed (left) and simulated (right) photon flux at 1.7 GeV (top), 13.6 GeV (middle), and 108.6 GeV (bottom).\
           Note that the panels on left side are diffuse (i.e. no point-like component)\
           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
  }
  \label{fig__gammaRay}
\end{figure*}

\begin{figure}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{The observed (left) and simulated (right) photon flux at 1.7 GeV (top), 13.6 GeV (middle), and 108.6 GeV (bottom).\
           Note that the panels on left side are diffuse (i.e. no point-like component)\
           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
  }
  \label{fig__gammaRay}
\end{figure}

>>>>

  As stressed by \citet{Yang2012}, CR diffusion has an insignificant effect on the overall morphology of the Fermi bubbles,\
  but only sharpens the edges of the simulated bubbles by the interplay between anisotropic CR diffusion\
  and magnetic fields with suppressed perpendicular diffusion across the bubble surface. Moreover,\
  the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
  a little effect on the overall dynamics. For these two reasons,\
  we have ignored the CR diffusion and the magnetic field throughout\
  the simulation.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different cases from left to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disk (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disk has an insignificant effect\
             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disk\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear associated with the disk, and without the disk, the outer bubbles will be tilted,
             indicating the dense disk is crucial for\
             the axis-symmetrically outer bubbles and of the most inner bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

@@

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center and observed by the poistion of the Sun.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disk normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
  \caption{The observed (left) and simulated (right) photon flux at 108.6 GeV.\
           Note that the panel on left side is diffuse (i.e. no point-like component)\
           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
  }
  \label{fig__gammaRay}
\end{figure*}

\begin{figure}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated spectra of the Fermi bubbles calculated for a longitude range of\
      $l=[-10^{\circ},10^{\circ}]$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.
  }
  \label{fig__gammaRay}
\end{figure}
